---
title: "Data"
---

Throughout the course we will make use of he [`experimentdatar`](https://itamarcaspi.github.io/experimentdatar/) data package that contains publicly available datasets that were used in Susan Athey and Guido Imbens' course ["Machine Learning and Econometrics"](https://www.aeaweb.org/conference/cont-ed/2018-webcasts) (AEA continuing Education, 2018). The datasets are conveniently packed for R users.

### Installation

You can install the **development** version from
[GitHub](https://github.com/itamarcaspi/experimentdatar/)

```r
# install.packages("devtools")
devtools::install_github("itamarcaspi/experimentdatar")
```

### Usage

Load the __experimentdatar__ package
```{r load_package, message=FALSE, warning=FALSE}

library(experimentdatar)

```

Load the `social` dataset

```{r load_data}

data(social)  

```

(You can find information about variable definitions using `?social`.)

Use `dataDetails()` function to open the paper associated with the `social` dataset

```{r details, eval=FALSE}
dataDetails("social")
```

Load the __dplyr__ and display the response (`outcome_vote`) and treatment variable (`treat_neighbors`)

```{r tibble, message=FALSE, warning=FALSE}
library(dplyr) # for data manipulations

social %>% 
  select(outcome_voted, treat_neighbors) %>% 
  head()
```

Use __ggplot2__ to plot the distribution of the median income of survey participants

```{r plot, message=FALSE, warning=FALSE}
library(ggplot2) # for generating plots

social %>% 
  ggplot(aes(median_age)) +
  geom_histogram(binwidth = 1)

```





### List of available datasets

* `charitable`: Data used for the paper "Does Price matter in charitable giving? Evidence from a large-Scale Natural Field experiment"  
by Karlan and List (2007).

* `IVdataset`: Data used for the paper "Does compulsory school attendance affect schooling and earnings?"  
by Angrist and Krueger (1991) and related papers.

* `mobilization`: Data for the paper "Comparing Experimental and Matching Methods Using a Large-Scale Voter Mobilization Experiment"  
by Arceneaux, Gerber, and Green (2006).

* `vouchers`: Data for the paper "Vouchers for Private Schooling in Colombia: Evidence from a Randomized Natural Experiment"  
by Angrist, Bettinger, Bloom, King, and Kremer (2002).

* `secrecy`: Data for the paper "Ballot Secrecy Concerns and Voter Mobilization: New Experimental Evidence about Message Source, Context, and the Duration of Mobilization Effects"  
by Gerber, Hubers, Biggers, and Hendry (2014).

* `social`: Data for the paper "Social Pressure and Voter Turnout: Evidence from a Large-Scale Field Experiment"  
by Gerber, Green, and Larimer (2008).

* `welfare`: Data for the paper "Modeling heterogeneous treatment effects in survey experiments with Bayesian Additive Regression Trees"  
by Green and Kern (2012).


### Resources

* The [ExperimentData repository](https://github.com/gsbDBI/ExperimentData) where you can find the original as well as new datasets and more documentations.