---
title: "Lasso prediction using mlr"
author:
  name: Itamar Caspi
  affiliation: ml4econ @ HUJI 2019
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    theme: flatly
    highlight: haddock 
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

## Introduction

In what follows, we will use the "Boston Housing Data" to train and test machine learning models learned in the course. In particular, we will apply the lasso algorithm to predict Boston area median house values based on a set of area specific features.

```{r remedy001}

set.seed(1203)

```
 
## Load dependencies
```{r}

if (!require("pacman")) install.packages("pacman")
pacman::p_load(mlr, glm)

```

## Read and clean data

```{r remedy002}

train     <- read.csv("data/train.csv")
test      <- read.csv("data/test.csv")
test$medv <- 0
testID    <- test$ID
train$ID  <- test$ID <- NULL


```

## Define the task

```{r remedy003}

trainTask <- makeRegrTask(data = train, target = "medv")
testTask  <- makeRegrTask(data = test, target = "medv")


```

## Preprocessing

Explain which preprocessing steps you take and why

```{r remedy004}

train$rad  <- as.factor(train$rad)
test$rad   <- as.factor(test$rad)
trainTask  <- createDummyFeatures(trainTask)
testTask   <- createDummyFeatures(testTask)
trainTask  <- normalizeFeatures(trainTask)
testTask   <- normalizeFeatures(testTask)


```

## Define the learner

Explain which algorithm you choose and why

```{r remedy005}

lrn <- makeLearner("regr.glmnet")

```

## Tune hyperparameter(s)

Discuss the process of tuning your algorithm's hyper parameters

```{r remedy006}

ps <- makeParamSet(
  makeNumericParam("s", lower = -5, upper = 2, trafo = function(x) 10^x)
)
ctrl  <- makeTuneControlRandom(maxit = 100L)
rdesc <- makeResampleDesc("CV", iters = 10L)
res   <- tuneParams(lrn, trainTask, rdesc, measures = mse, par.set = ps, control = ctrl)


```

## Fit the model


```{r remedy007}

lrn    <- setHyperPars(makeLearner("regr.glmnet"), par.vals = res$x)
model  <- train(lrn, trainTask)


```

## Make predictions

```{r remedy008}

pred   <- predict(model, testTask)
preds  <- pred$data$response


```

## Create submission file

```{r remedy009}

submission       <- data.frame(ID = testID)
submission$medv  <- preds

head(submission)
```
 
 
## Export prediction to a csv file
```{r}
write.csv(submission, "output/lassoSubmission.csv", row.names = FALSE)
```
