---
title: "Basic Concepts"
author: "Itamar Caspi"
date: '2019'
output:
  ioslides_presentation:
    df_print: tibble
    highlight: espresso
    css: style.css
  beamer_presentation:
    highlight: espresso
    includes:
      in_header: preamble.txt
    df_print: kable
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

## R Markdown

This is an \alert{R Markdown} presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
head(cars)
```

## Bias-Variance Tradeoff

$$y = ax+b+e$$
where $y$ is the response variable...

## Slide with Plot

```{r pressure}
plot(pressure)
```

## New Slide


